---
title: "DMT1 vs Controls "
author: "Jordi Real"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())
#memory.size(max=4000)
library("SNPassoc")
library("htmlwidgets")
library("compareGroups")
library("foreign")
library("lattice")
library("Hmisc")
#library("ggplot2")
library("pander")
library("readxl")
library("knitr")
#library("rmarkdown")
library("data.table")

```

##  Seleccionar controles para cada tipo de diabetes (edad y sexo)

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}

####  Llegir dades    #####

setwd ("G:/Google Drive/CIBERDEM/ESMERALDA/LIPOS_DIABETICOS")

load("Analisis_DM1vsControls")

```

# Table 1. Clinical and demographic characteristics of patients

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}

propensityDM1



export2md(taula3)


```


# Table 2. LIPOS diferences between presence of type 1 diabetes and controls

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}

export2md(taula2)

print("p valors ajustats")
# The "BH" (aka "fdr") and "BY" method of Benjamini, Hochberg, and Yekutieli control the false discovery rate, 


kable(pvalstaula1)



```

# Table 3. OR adjusted of presence of type 1 diabetic and controls

Adjusted by: 

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}

print(variablesajust1)

kable(ajustats,digits=3,caption="OR and p-value adjusted")


```

# Excluimos los pacientes dislipemicos

## No Dislipemicos 

# Table 2.1. Clinical and demographic characteristics of patients without dislipemia

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}

export2md(taula3NODL)

```

# Table 2.2. LIPOS diferences between presence of type 1 diabetes and controls

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge",results='asis'}

export2md(taula1.NODLP)

kable(pvalstaulaNODSL,digits=3)


```

# Table 2.3. LIPOS diferences between presence of type 1 diabetes and controls (adjusted)

Ajustado por: 

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge",results='asis'}

print(variablesajust2)


kable(ajustatsNODL,digits=3)



```



